\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Smoothing out wording in Secs 6.2-7.3.

\subsection{Testing Pipeline} 
We began by performing a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons.
A cognitive walkthrough is a formal method of inspection performed by researchers without any user involvement.
We then conducted qualitative and quantitative usability tests.
We believe both methods were necessary for a complete usability evaluation.
Qualitative testing illuminates {\it why or how} the software is or is not usable, while quantitative testing measures {\it to what extent}.
We used our qualitative study observations to design interface changes that would address encountered issues.
We used quantitative testing to measure the impact of our proposed changes, as compared to the original interface.

@@

\begin{itemize}
\item{reduced the amount of text and technical terms in the text (Figures~\ref{fig:new-first},~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge},~\ref{fig:new-bridge-combobox}, and ~\ref{fig:new-progress})  to encourage users to read instructions.} 
\item{centered the text to make the design compatible for left to right and right to left languages.}
\item{clarified that configuration options were manual and for heavily censored environments (Figure~\ref{fig:new-first}) to discourage users who did not need bridges and proxies from configuring them.}
\item{added a status bar on the proxy and bridge screens (Figure~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge}, and~\ref{fig:new-bridge-combobox}) to hint at future tasks.}
\item{reordered proxy and bridge screens (Figures ~\ref{fig:new-proxy} and ~\ref{fig:new-nobridge}) in a topologically sequential order. This hints that proper proxy configuration is necessary to reach bridges.}
\item{eliminated the bridge and proxy questions (Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy}) to reduce the number of screens.}
\item{added auto-detection for proxies (Figure~\ref{fig:new-proxy}) in place of the proxy question. In theory, this can be done locally without infrastructural changes or leaking information to the network.}
\item{added the option to not use a bridge on the bridge screen (Figures~\ref{fig:new-nobridge}, ~\ref{fig:new-bridge} and ~\ref{fig:new-bridge-combobox}) to replace the function of the of the bridge question screen (Figure~\ref{fig:old-bridge}).}
\item{gave a recommendation to use one of the three \texttt{meek}-transport bridges (Figure~\ref{fig:new-bridge}) in case the recommended \texttt{obfs3}-transport bridges were unreachable, which happens in heavily censored real environments and our simulated environment E3.}
\item{added a summary screen (Figure~\ref{fig:new-summary}) that summarizes the settings before making a connection to Tor, since some participants from the previous study didn't know how they connected to Tor.}
\item{added indicators on the progress screen (Figure~\ref{fig:new-progress}) that visualized what components are trying to be reached, and in the case of failure, showed which component was unreachable. This was to help users understand what was going on during  connection and to help troubleshoot their configuration.}
\end{itemize}

Our interface was made to test changes in a laboratory testing. We acknowledge that our version would need refining (aligning text properly, using higher quality visual assets, etc.) before deployment.

\section{Quantitative Testing}
\label{sec:quantitative}
We conducted our quantitative experiments at a behavioral laboratory with many participants in parallel, using instrumentation to capture evaluation metrics. We confirmed prior stumbling points and user behaviors and validated our proposed design improvements.

@@

\subsection{Procedure}
We ran our experiment at Xlab~\cite{xlab}, an experimental social science laboratory. Xlab had 36 workstations with identical Windows~7 laptops, with workstation partitions to discourage participants from looking at others' screens. At the beginning of each session, we used a script to revert the computers to a clean image; download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with or without our proposed UI changes); set up one of the three simulated environments (E1, E2, or E3); and start recording the computer screen. We manually assigned interface--environment combinations to each computer.

@@

\subsection{Results} 
In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}). As seen in Table~\ref{table:participant-summary}, our design changes helped more users connect to Tor in less time. However, many, including participants who used the redesigned version, still could not connect to Tor: 63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed. Those that managed to connect took long to do so (>3 minutes in E2 and >20 minutes in E3). Figure~\ref{fig:all-participant-edges} summarizes each participant---showing if they connected to Tor, how long they took to do so, and where they spent their time. Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.

>>>>

\subsection{Testing Pipeline} 
We began by performing a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons.
A cognitive walkthrough is a formal method of inspection performed by researchers without any user involvement.
We then conducted qualitative and quantitative usability tests.
We believe both methods were necessary for a complete usability evaluation.
Qualitative testing illuminates {\it why or how} the software is or is not usable, while quantitative testing measures {\it to what extent}.
We used our observations from the qualitative study to design interface changes that would address common issues that participants encountered.
We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original interface.

@@

\begin{itemize}
\item{reduced the amount of text and technical terms in the text (Figures~\ref{fig:new-first},~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge},~\ref{fig:new-bridge-combobox}, and ~\ref{fig:new-progress})  to encourage users to read instructions.} 
\item{centered the text to make the design compatible for left to right and right to left languages.}
\item{clarified that configuration options were manual and for heavily censored environments (Figure~\ref{fig:new-first}) to discourage users who did not need bridges and proxies from configuring them.}
\item{added a status bar on the proxy and bridge screens (Figure~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge}, and~\ref{fig:new-bridge-combobox}) to hint at future tasks.}
\item{reordered proxy and bridge screens (Figures ~\ref{fig:new-proxy} and ~\ref{fig:new-nobridge}) in a topologically sequential order. This hints that proper proxy configuration is necessary to reach bridges.}
\item{eliminated the bridge and proxy questions (Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy}) to reduce the number of screens.}
\item{added auto-detection for proxies (Figure~\ref{fig:new-proxy}) in place of the proxy question. In theory, this can be done locally without infrastructural changes or leaking information to the network.}
\item{added the option to not use a bridge on the bridge screen (Figures~\ref{fig:new-nobridge}, ~\ref{fig:new-bridge} and ~\ref{fig:new-bridge-combobox}) to replace the function of the bridge question screen (Figure~\ref{fig:old-bridge}).}
\item{added a recommendation to use one of the three \texttt{meek}-transport bridges (Figure~\ref{fig:new-bridge}) if the recommended \texttt{obfs3}-transport bridges were unreachable, which happens in heavily censored real environments and our simulated environment E3.}
\item{added a summary screen (Figure~\ref{fig:new-summary}) that summarizes the settings before making a connection to Tor, since some participants from the previous study didn't know how they connected to Tor.}
\item{added indicators on the progress screen (Figure~\ref{fig:new-progress}) that visualized what components are trying to be reached, and in the case of failure, showed which component was unreachable. This was to help users understand what was going on during  connection and to help troubleshoot their configuration.}
\end{itemize}

Our interface was intended as a proof of concept, so we could evaluate these changes in a laboratory testing. We acknowledge that further refinement (aligning text properly, using higher quality visual assets, etc.) would be needed before deployment.

\section{Quantitative Testing}
\label{sec:quantitative}
We conducted our quantitative experiments at a behavioral laboratory with many participants in parallel, using instrumentation to capture evaluation metrics. These experiments confirmed previously-seen stumbling points and user behaviors and validated our proposed design improvements.

@@

\subsection{Procedure}
We ran our experiment at Xlab~\cite{xlab}, an experimental social science laboratory. Xlab had 36 workstations with identical Windows~7 laptops, with workstation partitions to discourage participants from looking at others' screens. At the beginning of each session, we used a script to revert the computers to a clean image; download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with or without our proposed UI changes); set up one of the three simulated environments (E1, E2, or E3); and start recording the computer screen.
We assigned each participant to one of six conditions (Table~\ref{table:participant-summary}), which determines their user interface (OLD or NEW) and censorship environment (E1, E2, or E3).
We use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}).

@@

\subsection{Results} 
As seen in Table~\ref{table:participant-summary}, our design changes helped more participants connect to Tor in less time. However, many participants, including participants who used the new interface, still could not connect to Tor: 63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed. Those who managed to connect often took a long time to do so (>3 minutes in E2 and >20 minutes in E3). Figure~\ref{fig:all-participant-edges} summarizes each participant, showing whether they successfully connected to Tor, how long they took to do so, and where they spent their time. Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.
